Active Learning for SAT Solver Benchmarking

### 2022-10-14 paper/paper.tex
Regenerate pdf

\author{
  Author(s) anonymized for review
  \vspace{0.4cm}
}

\institute{
  Institute(s) anonymized for review
  \vspace{0.4cm}
}

@@

The posed \emph{New-Solver Problem} has stark similarities to the well-studied field of active learning (AL) within recommender systems, in particular the \emph{new-user problem}~\cite{RubensESK15}.
On the one hand, we want to maximize the utility an instance provides to our model, i.e., rank prediction accuracy, and on the other hand, minimize the cost, i.e., runtime, that is associated with its acquisition.
In contrast to traditional passive machine-learning methods with given instance labels, active learning allows for selecting instances for which to acquire labels.
AL algorithms can be categorized into \emph{synthesis-bas\-ed} \cite{0001AEMN22,GarzonMG22,2019gaal} and \emph{pool-bas\-ed} approaches \cite{GolbandiKL11,HarpaleY08,KorenBV09}.
While synthesis-based methods generate instances for labeling, pool-based methods rely on a fixed set of unlabeled instances from which to sample.

>>>>

\author{
  Author(s) anonymized for review
  \vspace{1.0cm}
}

\institute{
  Institute(s) anonymized for review
  \vspace{0.8cm}
}

@@

The posed \emph{New-Solver Problem} has stark similarities to the well-studied field of active learning (AL) within recommender systems, in particular, the \emph{new-user problem}~\cite{RubensESK15}.
On the one hand, we want to maximize the utility an instance provides to our model, i.e., rank prediction accuracy, and on the other hand, minimize the cost, i.e., runtime, that is associated with its acquisition.
In contrast to traditional passive machine-learning methods with given instance labels, active learning allows for selecting instances for which to acquire labels.
AL algorithms can be categorized into \emph{synthesis-bas\-ed} \cite{0001AEMN22,GarzonMG22,2019gaal} and \emph{pool-bas\-ed} approaches \cite{GolbandiKL11,HarpaleY08,KorenBV09}.
While synthesis-based methods generate instances for labeling, pool-based methods rely on a fixed set of unlabeled instances from which to sample.
